A Switching Planner for Combined Task and Observation Planning

### 2011-02-09 subarchitectures/planner.sa/trunk/src/latex/AAAI11/evaluation.tex
few small changes

We compare switching to the {\em baseline} in several realistic
tasks, with the number of rooms ranging from 3 (12-places, 16-objects,
$|$states$|$ $>10^{21}$) to 6 (26-places, 21-objects, $|$states$|$
$>10^{36}$). We also compare those systems with near optimal policies
computed using Smith's {\sc zmdp} for small 2 room problems (4-places,
3-objects, $|$states$|$ $\simeq 5000$). Our evaluation considers 3
levels of reliability in sensing: {\em reliable} sensors have a $.1$
probability of a false negative, {\em semi-reliable} have a chance of
$0.3$ of false negative and $0.1$ of false positive , and {\em noisy}
sensors with probabilities of $0.5$ and $0.2$ respectively. Each
object class is assigned one sensor model -- e.g. cornflakes may be
harder to detect than refrigerators. We performed several experiments
with different levels of reliability for sensing the target object(s),
while keeping sensing models for non-target objects constant.

\Omit{
All non-target objects remain unchanged so the planner can
exploit object co-occurances using reliably sensed objects to
compensate for the increased sensor noise.
}

We experimented with DT sessions with initial belief-states admitting
between 20 and 100 abstract states with non-zero probability. We run
50 simulations in each configuration, and have a timeout on each
simulation of 30 minutes (1800 seconds)\footnote{All experiments were
conducted on a 2.66GHz Intel Xeon X5355 using one CPU core.}. The
continual planning times are reported in
Figure~\ref{fig:results-time}, and the quality data in
Figure~\ref{fig:results-quality}.
%%
For each task, the goal is to find one or more objects and report
their position to a user. Usually there is a non-zero probability that
no plan exists, as the desired object might not be present in the
environment.
% MOG: I didn't do  evaluations for those, so let's remove them
% Item~$f$ reports for tasks requiring indirect sensing,
% where the robot must relocate to a room with a particular category
% (e.g. kitchen). the {\em baseline} is not able to complete Item~$f$,
% so is omitted from that reporting.  
Because reward is only allocated on the achievement of a goal, we
find it intuitive to report average plan costs and the success rates
in problems that admit a solution (i.e., positive reward scaled by a
constant factor).

@@

We find that if sensing is reliable, then little is gained using DT
sessions, as the greedy approach of the {\em baseline} is
sufficient. As sensing degrades DT sessions prove more useful. Here,
time spent on DT planning increases steeply as the abstraction becomes
more refined, which is compensated for by fewer planning sessions
overall. More detailed abstractions lead to a better overall
success rate, particularly for tasks $d$ and $e$.
%% Moreover,
%% for less refined abstractions, the increased cost of DT planning is
%% partially compensated for by a decrease in Fast Downward planning
%% times. 
Speaking to the effectiveness of our entropy heuristic for abstraction
refinement, we witness relatively high success rates irrespective of
the exact level of refinement. Comparing finally to the best {\sc
zmdp} policy, although producing relatively costly plans, the
continual planners performed quite well, especially in terms success
rate. A key source of inefficiency here, is due to sequential sessions
always being optimistic, and refusing to abandon the search.

>>>>

We compare switching to the {\em baseline} in several realistic
tasks, with the number of rooms ranging from 3 (12-places, 16-objects,
$|$states$|$ $>10^{21}$) to 6 (26-places, 21-objects, $|$states$|$
$>10^{36}$). We also compare those systems with near optimal policies
computed using Smith's {\sc zmdp} for small 2 room problems (4-places,
3-objects, $|$states$|$ $\simeq 5000$). Our evaluation considers 3
levels of reliability in sensing: {\em reliable} sensors have a $.1$
probability of a false negative, {\em semi-reliable} have a chance of
$0.3$ of false negative and $0.1$ of false positive, and {\em noisy}
sensors with probabilities of $0.5$ and $0.2$ respectively. Each
object class is assigned one sensor model -- e.g. cornflakes may be
harder to detect than refrigerators. We performed several experiments
with different levels of reliability for sensing the target object(s),
while keeping sensing models for non-target objects constant.

\Omit{
All non-target objects remain unchanged so the planner can
exploit object co-occurrences using reliably sensed objects to
compensate for the increased sensor noise.
}

Our evaluation examines DT sessions with initial belief-states
admitting between 20 and 100 abstract states with non-zero
probability. We run 50 simulations in each configuration, and have a
timeout on each simulation of 30 minutes (1800 seconds)\footnote{All
experiments were conducted on a 2.66GHz Intel Xeon X5355 using one CPU
core.}. The continual planning times are reported in
Figure~\ref{fig:results-time}, and the quality data in
Figure~\ref{fig:results-quality}.
%%
For each task, the goal is to find one or more objects and report
their position to a user. Usually there is a non-zero probability that
no plan exists, as the desired object might not be present in the
environment.
% MOG: I didn't do  evaluations for those, so let's remove them
% Item~$f$ reports for tasks requiring indirect sensing,
% where the robot must relocate to a room with a particular category
% (e.g. kitchen). the {\em baseline} is not able to complete Item~$f$,
% so is omitted from that reporting.  
In these experiments we only allocate reward on the achievement of all
goals, therefore we find it intuitive to report average plan costs and
the success rates in problems that admit a complete solution (i.e.,
positive reward scaled by a constant factor). The exception occurs for
items f and g of Figure~\ref{fig:results-quality}, where we report the
overall success rate of the respective approaches.

@@

We find that if sensing is reliable, then little is gained using DT
sessions, as the greedy approach of the {\em baseline} is
sufficient. As sensing degrades DT sessions prove more useful. Here,
time spent on DT planning increases steeply as the abstraction becomes
more refined, which is compensated for by fewer planning sessions
overall. More detailed abstractions lead to a better overall
success rate, particularly for tasks $d$ and $e$.
%% Moreover,
%% for less refined abstractions, the increased cost of DT planning is
%% partially compensated for by a decrease in Fast Downward planning
%% times. 
Speaking to the effectiveness of our entropy heuristic for abstraction
refinement, we see relatively high success rates irrespective of
the level of refinement. Comparing finally to the best {\sc
zmdp} policy, although producing relatively costly plans, the
continual planners performed quite well, especially in terms success
rate. A key source of inefficiency here, is due to sequential sessions
always being optimistic, and refusing to abandon the search.
